\NAME: A framework for \\ Efficient Intrusion Detection\\ in the Internet of Things

### 2014-10-22 paper.tex
fixed heartbeat/watchdog issues + listings order

The DSL enables researchers to formally describe their ID algorithms, without
focusing on any specific language or platform. Given such formal descriptions
of ID algorithms, a code generator is now able to combine these, while avoiding
the problems arising from the patterns/problems presented in listings
\ref{alg:id-algo-application} and \ref{alg:id-algo-pattern}. It can also target
different languages and platforms, while reusing a software library that
provides e.g. message parsing, network access wrapping,\dots

@@

Three criteria were evaluated: the image size of the resulting compiled code,
the network usage in number of frames and bytes and the time required to
perform once cycle of the event loop. These metrics were collected in four
situations: without ID algorithms, with a heartbeat, with reputation-tracking
and with both algorithms implemented.

@@

\begin{table}[H]
  \centering
  \begin{tabular}{lrrrr}
  \hline
      & base & heartbeat & reputation & both\\
  \hline
  size (bytes) & 10500 & 148\% & 127\% & 175\%\\
  frames & 20 & 255\% & 160\% & 315\%\\
  bytes & 476 & 406\% & 181\% & 487\%\\
  time ($\mu$s) & 48 & 196\% & 183\% & 310\%\\
  \hline
  \end{tabular}
  \caption{Results for the manual implementation.}
  \label{tbl:manual}
\end{table}

\begin{table}[H]
  \centering
  \begin{tabular}{lrrrr}
  \hline
         & base & heartbeat & reputation & both\\
  \hline
  size (bytes) & 10496 & 175\% & 156\% & 200\%\\
  frames & 20 & 245\% & 160\% & 275\%\\
  bytes & 476 & 399\% & 186\% & 454\%\\
  time ($\mu$s) & 48 & 252\% & 252\% & 288\%\\
  \hline
  \end{tabular}
  \caption{Results for the generated implementation.}
  \label{tbl:generated}
\end{table}

@@

\begin{table}[H]
  \centering
  \begin{tabular}{lrrrrr}
  \hline
                & base & heartbeat & reputation & both  & result \\
  \hline
  size (bytes)  & -4    & 2822     & 3070       & 2664  & 115\%  \\
  frames        & 0     & -2       & 0          & -8    & 87\%   \\
  bytes         & 0     & -36      & 24         & -156  & 93\%   \\
  time ($\mu$s) & 0     & 27       & 33         & -11   & 93\%   \\
  \hline
  \end{tabular}
  \caption{Comparison of both implementations.}
  \label{tbl:summary}
\end{table}

>>>>

The DSL enables researchers to formally describe their ID algorithms, without
focusing on any specific language or platform. Given such formal descriptions
of ID algorithms, a code generator is now able to combine these, while avoiding
the problems arising from the patterns/problems presented in listings
\ref{alg:id-algo-pattern} and \ref{alg:id-algo-application}. It can also target
different languages and platforms, while reusing a software library that
provides e.g. message parsing, network access wrapping,\dots

@@

Three criteria were evaluated: the image size of the resulting compiled code,
the network usage in number of frames and bytes and the time required to
perform once cycle of the event loop. These metrics were collected in four
situations: without ID algorithms, with a watchdog, with reputation-tracking
and with both algorithms implemented.

@@

\begin{table}[H]
  \centering
  \begin{tabular}{lrrrr}
  \hline
      & base & watchdog & reputation & both\\
  \hline
  size (bytes) & 10500 & 148\% & 127\% & 175\%\\
  frames & 20 & 255\% & 160\% & 315\%\\
  bytes & 476 & 406\% & 181\% & 487\%\\
  time ($\mu$s) & 48 & 196\% & 183\% & 310\%\\
  \hline
  \end{tabular}
  \caption{Results for the manual implementation.}
  \label{tbl:manual}
\end{table}

\begin{table}[H]
  \centering
  \begin{tabular}{lrrrr}
  \hline
         & base & watchdog & reputation & both\\
  \hline
  size (bytes) & 10496 & 175\% & 156\% & 200\%\\
  frames & 20 & 245\% & 160\% & 275\%\\
  bytes & 476 & 399\% & 186\% & 454\%\\
  time ($\mu$s) & 48 & 252\% & 252\% & 288\%\\
  \hline
  \end{tabular}
  \caption{Results for the generated implementation.}
  \label{tbl:generated}
\end{table}

@@

\begin{table}[H]
  \centering
  \begin{tabular}{lrrrrr}
  \hline
                & base & watchdog & reputation & both  & result \\
  \hline
  size (bytes)  & -4    & 2822     & 3070       & 2664  & 115\%  \\
  frames        & 0     & -2       & 0          & -8    & 87\%   \\
  bytes         & 0     & -36      & 24         & -156  & 93\%   \\
  time ($\mu$s) & 0     & 27       & 33         & -11   & 93\%   \\
  \hline
  \end{tabular}
  \caption{Comparison of both implementations.}
  \label{tbl:summary}
\end{table}
